MSAD_PCA_Walkthrough

### 2017-01-25 Simulation_Vignette.Rmd
Returned the n calculation within the while() loop of processMonitor to its original value. I need to think about why I did that the way I did. Further, we resolved the off-by-one error: the "date/" subset operation for xts objects is the "date" and all following rows, rather than all rows following "date". This caused "date" to be counted twice for each run of the while() loop.

# Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
falseAlarmRate_SPE <- sum(results_ls$FaultChecks[,5] %in% c(2,3)) /
  nrow(results_ls$FaultChecks)
# The SPE false alarm rate hits 0 at alpha = 0.07.
falseAlarmRate_T2 <- sum(results_ls$FaultChecks[,5] %in% c(1,3)) /
  nrow(results_ls$FaultChecks)
# The T2 false alarm rate hits 0 at alpha = 0.00015, and is at 16% at 0.07. The
# T2 statistic throws too many false alarms for my taste.
# These values were before we split the update observations by a third. These
# false alarm rates increased dramatically (0.19, 0.41), so we increased the 
# number of training observations to 4320 (three days worth, up from 2880). The
# false alarm rates dropped back, but not nearly as low (0.0031, 0.0884).

# CURRENT ISSUE: The number of alarmed and non-alarmed observations does not
# sum to 10080 - trainObs. For 2880 training observations, the sum of alarmed
# and non-alarmed observations was 83 + 4195 = 4278 < 10080 - 2880 = 7200,
# while for 4320 training observations, the sum was 506 + 5256 = 5762 > 10080 -
# 4320 = 5760. What in the actual hell?
```

>>>>

# Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
falseAlarmRate_SPE <- sum(results_ls$FaultChecks[,5] %in% c(2,3)) /
  nrow(results_ls$FaultChecks)
# The SPE false alarm rate hits 0 at alpha = 0.07.
falseAlarmRate_T2 <- sum(results_ls$FaultChecks[,5] %in% c(1,3)) /
  nrow(results_ls$FaultChecks)
# The T2 false alarm rate hits 0 at alpha = 0.00015, and is at 16% at 0.07. The
# T2 statistic throws too many false alarms for my taste.
# These values were before we split the update observations by a third. These
# false alarm rates increased dramatically (0.19, 0.41), so we increased the 
# number of training observations to 4320 (three days worth, up from 2880). The
# false alarm rates dropped back, but not nearly as low (0.0031, 0.0884).
```
